Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-06-29 docs/ms_sageAbundance.Rmd
adds knots figure to ms

@@

where $d_{s,m}$ is the Euclidean distance between the centroid of sample cell \emph{s} and the location of knot \emph{m}, and $\sigma$ is the kernel bandwidth. It is possible through exhaustive model selection and fitting to determine the optimal form of the kernel and to estimate optimal values for $\sigma$. However, given the relative largeness of our dataset and computational limitations, we decided to to create kernels around eight knots and used a rule-of-thumb to set $\sigma$ equal to the distance between nearest neighbor knots (Higdon 2002, Conn et al. 2014).

@@

>>>>

```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

# PDF-based figures
opts_chunk$set(dev='pdf')
```

@@

where $d_{s,m}$ is the Euclidean distance between the centroid of sample cell \emph{s} and the location of knot \emph{m}, and $\sigma$ is the kernel bandwidth. It is possible through exhaustive model selection and fitting to determine the optimal form of the kernel and to estimate optimal values for $\sigma$. However, given the relative largeness of our dataset and computational limitations, we decided to to create kernels around 81 knots (Figure #) and used a rule-of-thumb to set $\sigma$ equal to the distance between nearest neighbor knots (Higdon 2002, Conn et al. 2014).

@@

Figures
-------
```{r figure_1,dependson="plot-options", fig.cap="Average percent cover or each grid cell of the study area with knots used for spatial convolution in dimension reduction.", fig.height=6}
library(png)
library(grid)
img <- readPNG("components/figure/SAGE_Grid_wKnots.png")
grid.raster(img)
